Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Do not bold this text

These R-derived Markdown files, if committed and pushed, then enjoy the usual privileged treatment on GitHub already described above. Once an `.Rmd` file has been rendered to `.md`, anyone viewing it on GitHub can read the prose, study the R code, __and view the results of running that code__, including figures. Figure \ref{fig:report-from-r-or-rmd}C shows how the `.Rmd` document from Figure \ref{fig:report-from-r-or-rmd}A looks when rendered to `.md` and pushed to GitHub. It is the best of all worlds, because the code is revealed and, by definition, is the code that produced the results. And yet a reader can gaze upon the product in a web browser, without needing to download the code, install all necessary dependencies, and run it.

>>>>

These R-derived Markdown files, if committed and pushed, then enjoy the usual privileged treatment on GitHub already described above. Once an `.Rmd` file has been rendered to `.md`, anyone viewing it on GitHub can read the prose, study the R code, and view the results of running that code, including figures. Figure \ref{fig:report-from-r-or-rmd}C shows how the `.Rmd` document from Figure \ref{fig:report-from-r-or-rmd}A looks when rendered to `.md` and pushed to GitHub. It is the best of all worlds, because the code is revealed and, by definition, is the code that produced the results. And yet a reader can gaze upon the product in a web browser, without needing to download the code, install all necessary dependencies, and run it.
